---
title: "Predicting Exercise Performance Using Machine Learning"
author: "Khotami Fitri Karimah"
date: "24/02/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Using data from accelerometers, we predict the manner in which individuals perform weightlifting exercises. The target variable is `classe`, which indicates the correctness of the exercise execution.

## Load Libraries
```{r}
library(caret)
library(randomForest)
library(ggplot2)
library(dplyr)
```

## Load and Explore Data
```{r}
train_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
test_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

train_data <- read.csv(train_url, na.strings = c("NA", "", "#DIV/0!"))
test_data <- read.csv(test_url, na.strings = c("NA", "", "#DIV/0!"))

str(train_data)
summary(train_data)
```

## Data Preprocessing
```{r}
# Remove columns with many missing values
train_data <- train_data[, colSums(is.na(train_data)) == 0]

# Remove irrelevant columns (ID, timestamps, etc.)
train_data <- train_data %>% select(-c(1:7))

# Convert classe to factor
train_data$classe <- as.factor(train_data$classe)
```

## Split Data into Training and Validation Sets
```{r}
set.seed(123)
trainIndex <- createDataPartition(train_data$classe, p = 0.8, list = FALSE)
train_set <- train_data[trainIndex, ]
valid_set <- train_data[-trainIndex, ]
```

## Train a Random Forest Model
```{r}
set.seed(123)
rf_model <- randomForest(classe ~ ., data = train_set, ntree = 100)
```

## Model Evaluation
```{r}
pred_valid <- predict(rf_model, valid_set)
conf_matrix <- confusionMatrix(pred_valid, valid_set$classe)
conf_matrix
```

## Prediction on Test Data
```{r}
test_data <- test_data[, colnames(test_data) %in% colnames(train_set)]
test_predictions <- predict(rf_model, test_data)
test_predictions
```

## Conclusion
- **Random Forest performed well** on the validation set.
- **The model predicts the exercise performance** with high accuracy.
- **Predictions were made on 20 test cases.**
